The framing of active school travel in Ontario, Canada as a health and built environment issue

### 2021-12-01 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Discussion and conclusion completed, references updated

journal: "Social Science & Medicine"
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
linenumbers: false
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

@@

Rates of walking and bicycling to school, commonly known as active school travel (AST), have been declining in Canada and the United States for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013], Denmark [@jensenHowObtainHealthy2008], and Japan [@waygoodChapterSixteenJapan2020]. However, the appetite for AST may be high in many Canadian communities. For instance, 40% of children in a study conducted in Toronto, Ontario who are driven to school would like to travel by bicycle instead [@laroucheRatherBikeSchool2016a]. But the study reported that less than 3% actually do, despite the vast majority having access to a bicycle and living within a short and bikeable distance to school. Another study based in London, Ontario reported similar findings with respect to children's preference for active travel [@larsenRouteBasedAnalysisCapture2012]. From a public health perspective, this represents a huge opportunity to improve health and wellbeing if more children could use active modes to school.

In response to this trend, the Government of Ontario, in Canada, created a fund in 2017 to support communities across the province in developing AST initiatives. Green Communities Canada runs the program, called _Ontario Active School Travel_, and determines the projects that will be funded with their support [@GreenCommunities2016]. As of December 2021, OAST has funded and provided resources for over 20 projects across Ontario.  Many communities implemented school travel planning (STP), along with encouragement activities like walking school buses or developed resources for schools and parents, among other actions [see @GreenCommunitiesProjects]. In this context, STP is a popular "school-specific" intervention led by a facilitator that brings together a committee of stakeholders from diverse sectors including education, planning, transportation, and public health to develop action plans [@buliungSchoolTravelPlanning2011; @mammenSchoolTravelPlanning2014]. The five-step process involves identifying barriers to AST based on the local context and implementing approaches or activities following the 5 E's that alleviate concerns about AST and make AST safer and more convenient [@buliungSchoolTravelPlanning2011; @langUnderstandingModalChoice2011].

@@

More recently, there has been literature exploring the link between transport and children's wellbeing [@waygoodTransportChildrenWellbeing2020], with relevant applications to the study of travel satisfaction [@vandenbergFactorsAffectingParental2020; @westmanChildrenTravelSchool2017]. Being driven to school reduces community interactions for children which may impact their social wellbeing [@waygoodChildrenTravelIncidental2015], whereas walking and bicycling give children opportunities to socialize with friends or siblings [@michailChildrenExperiencesTheir2021]. This is something that children highly value about travel [@zwertsHowChildrenView2010a] and indicates that social connections through travel are important for their wellbeing. AST also provides opportunities for children to engage with the natural environment [@fuscoUnderstandingChildrenPerceptions2012; @romeroChildrenExperiencesEnjoyment2015] which can improve their mental or emotional wellbeing.

@@

At the individual level, older child age is often associated with AST [@mammenUnderstandingDriveEscort2012; @starkExploringIndependentActive2018; @wilsonUnderstandingChildParent2018] as parents typically escort younger children. There is some evidence that gender is a determinant of AST [@larsenInfluencePhysicalEnvironment2009], with boys being more likely to travel using active modes than girls, although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015]. Children's mode choice to school is strongly influenced by their parents' travel behaviours and the complexity of their household's travel needs [@buliungLivingJourneySchool2021], which indicates that shifting parental perceptions and habits is important. Convenience and inclement weather have been cited by parents as barriers to AST [@buliungSchoolTravelPlanning2011]. Parental perceptions of the built or school environment [@demeesterParentalPerceivedNeighborhood2014; @panterAttitudesSocialSupport2010] and their children's skills [@ghekiereInsightsChildrenIndependent2017] also influence whether they allow their children to walk or bicycle to school.

Distance between home and school is most strongly associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school. Many studies have also found that the quality of the built environment along the route to school and around the school site [@ikedaAssociationsChildrenActive2018; @kimBuiltNaturalEnvironmental2020; @rothmanActiveSchoolTransportation2021] and provision of active travel infrastructure [@chenPromotingActiveStudent2018a; @pontEnvironmentalCorrelatesChildren2009] facilitate AST. Canadian youth report that they feel most safe bicycling on streets in their neighbourhood or that have low volumes of traffic [@TACbikeinfra2020]. Finally, concerns about traffic and strangers have been reported by parents who drive their children to school [@mammenUnderstandingDriveEscort2012], which highlights that the volume and speed of cars can be a concern or deterrent for AST.

@@

We assembled a collection of publicly available documents that were sourced online from the main stakeholder groups involved in STP initiatives in Ontario: i) school boards (public or Catholic and English-speaking only); ii) municipal governments; and iii) transportation consortia. The latter are a unique group of entities sanctioned by Ontario's Ministry of Education in Ontario 2006. Each consortium involves a collaboration between regions and school boards; the consortium's objective is to deliver more efficient and timely transportation services to schools in each region [@ministryeducation2006]. Non-profit organizations, police services, and advocacy groups are other stakeholders who often play a role in supporting AST and/or STP, but this study does not include any documents from these groups because they are not consistently participating in all initiatives across Ontario.

@@

kbl(text_tbl,
    booktabs = TRUE,
    caption = "\\label{tab:policy-concordance}CAPTION THIS TABLE") %>%
  kable_paper(full_width = F) %>%
  kable_styling(latex_options = c("striped")) %>%
  column_spec(1, bold = T) %>%
  column_spec(3, width = "20em")
```

@@

```{r topics-academic, include=FALSE, cache=TRUE}
# DO NOT RUN EVERY TIME - takes approximately 20 minutes

#academic_lda_num <- FindTopicsNumber(
  #academic_dtm, 
  #topics = seq(from = 2, to = 25, by = 1),
  #metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  #method = "Gibbs")
  #control = list(seed = 77),
  #mc.cores = 2L,
  #verbose = TRUE)
```

@@

FindTopicsNumber_plot(municipal_lda_num)
FindTopicsNumber_plot(school_lda_num)
FindTopicsNumber_plot(consortia_lda_num)
FindTopicsNumber_plot(policy_lda_num)
#FindTopicsNumber_plot(academic_lda_num)

@@

academic_lda <- LDA(academic_dtm, k = 17, method = "Gibbs", control = NULL, model = NULL)
```

@@

```{r policy-terms, echo=FALSE, out.width="1\\linewidth", fig.cap="\\label{fig:policy-terms}CAPTION THIS FIGURE"}
policy_top_terms <- policy_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -beta)

@@

```{r academic-terms, echo=FALSE, out.width="1\\linewidth", cache=TRUE, fig.cap="\\label{fig:academic-terms}CAPTION THIS FIGURE"}

@@

Finally, we conduct topic modelling to examine the different topics found in the policy and academic corpora. We focus on the policy corpus, instead of individually assessing the municipal, school, and consortia documents, so that we could report on the various frames used across all documents put out by STP stakeholder groups in Ontario. To determine the number of discrete topics in each corpus, we use the _ldatuning_ package. We then use the `LDA` function from the _topicmodels_ package to estimate an LDA model for each group of documents. The parameters from the _ldatuning_ package suggest that the policy corpus has between 7 and 9 topics and the academic corpus has between 17 and 25 topics. After running the LDA model for the academic corpus, it was too difficult to interpret a minimum of 17 topics based on the clusters of words that were identified. We experimented with the model by adjusting the number of topics and found that there were 9 distinct topics that could be interpreted, after which there was too much overlap. Figures \ref{fig:policy-terms} and \ref{fig:academic-terms} present the main terms that are associated with the topics found in each corpus.

In the policy corpus, we interpret the following topics based on the cluster of words: (1) resources for walking, (2) busing information and eligibility; (3) benefits of active travel; (4) bicycling and the environment; and (5) supporting active travel. These topics indicate that STP stakeholder groups are sending the message that walking and bicycling to school are healthy travel modes for students, particularly as a means to get physical activity. We also found that there is information shared to support parents and students in using active modes to school such as the availability of cycling lanes or route tips for walking.

The academic corpus has a higher number of topics likely due to the volume of papers that were sourced. The following topics were identified based on the clusters of words: (1) __unclear__ (2) AST in Ontario and Canada; (3) __unclear__; (4) children’s independent mobility; (5) safe routes to school programs; (6) commuting and distance; (7) density in the built environment and walking routes; (8) __unclear__; (9) walking interventions; (10) bicycling influences; (11) interpersonal and household influences on trips; (12) behaviours and attitudes; (13) __unclear__; (14) __unclear__; (15) walking distance; (16) __unclear__;  (17) physical activity measures or results; (18) bicycling attitudes; and (19) __unclear__.

@@

Finally, the policy documents discuss proposed solutions to encourage AST. STP stakeholder groups seem to be communicating that AST is possible and safe as a result of improvements to the built environment and available resources for parents and children. A final focus in the policy documents is on various efforts that are underway to support active travel including route planning.

@@

Using topic modelling, we analyzed how AST is framed in documents available to the general public on the websites of STP stakeholder groups in Ontario. We found that AST is primarily framed as beneficial to the health and wellbeing of children and to environmental sustainability. This was confirmed by the most common bigrams identified in the policy corpus, as well as the topics identified by the LDA model. The policy documents adequately reflect the evidence that AST contributes positively to children's physical health [see @faulknerActiveSchoolTransport2009; @schoeppeAssociationsChildrenActive2015]. STP stakeholder groups also communicate that increasing AST may reduce traffic near and around schools which could alleviate parental concerns about traffic safety. The potential outcomes of increased AST are highlighted which may be persuasive arguments to motivate behaviour change, which is the secondary frame of AST that we interpreted based on the LDA models.

The proposed solutions to the problem of declining AST that are communicated to the general public are mostly educational (e.g., safety tips or maps of safe routes) and engineering changes (e.g., traffic calming or bicycle lanes). These solutions have to sufficiently address real and perceived concerns that pose barriers to AST in order to encourage adoption. In most documents, the emphasis is on providing parents with resources that help them switch modes for the school commute and/or on reassuring them that the built environment has become safer and friendlier to active travelers.

However, the policy documents noticeably lacked a focus on individual and household level determinants of AST. For example, the role of convenience and inclement weather in shaping household travel decisions [@buliungSchoolTravelPlanning2011] or the age at which children become allowed to travel by active modes or independently [@mammenUnderstandingDriveEscort2012] were not discussed. Given the range of factors that influence AST in a Canadian setting [_inter alia_, see @mammenUnderstandingDriveEscort2012; @mitraIndependentMobilityMode2013; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], STP stakeholder groups must decide which points of intervention that they can reasonably have some influence towards. This should also depend on the local context so that barriers to AST as perceived by parents are addressed. It could be that STP stakeholder groups perceive to have more control over the micro-scale elements of the built environment, like traffic calming, rather than the ability to influence the number of trips to different destinations that households need to make. STP stakeholders are also unable to intervene in residential location, which affects distance to school.

To increase rates of walking and bicycling independently to school, Riazi et al. [-@riaziCorrelatesChildrenIndependent2019] state: "it will be vital for interventions to target modifiable factors, including children's and parents' perceptions of their social environment." We argue that STP messaging should also target multiple modifiable factors, in addition to the health and environmental benefits. Parents play the important role of "gatekeeper" by either granting or restricting their child's mobility [@sharminAssociationBuiltEnvironment2017]. For this reason, stakeholders involved in STP should produce more information that specifically responds to parents' perceived barriers and challenges. For example, STP materials could explain how known concerns in a particular municipality or school area have been addressed through local solutions.

@@

Many municipalities, schools, and transportation consortia use similar content in their public documents about AST. It would be worthwhile for STP stakeholders to adapt generic content so that it is more specific to factors associated with AST or parental perceptions about barriers to AST in the local context. Rothman et al. [-@rothmanDeclineActiveSchool2018a] note that local solutions to address specific school challenges are worthwhile, and we extend this recommendation to include local context in STP messaging about AST.

@@

@@

## 7.1. Future research

Future studies may investigate how parents and policy makers outside the field of public health respond to the ways in which AST is framed in STP documents. It would be helpful to know which frames would most encourage behaviour change or increase political support for interventions that address barriers to AST. This type of information could ensure that educational strategies and promotional materials increase buy-in for their target audience.

Acknowledgments
===================

This research was completed using open software, and the authors wish to acknowledge the developers of the following `R` packages: `dplyr` [@R-dplyr], `ggraph` [@R-ggraph], `ggplot2` [@R-ggplot2], `igraph` [@R-igraph], `pdftools` [@R-pdftools], `readr` [@R-readr], `reshape2` [@R-reshape2], `stringr` [@R-stringr], `text2vec` [@R-text2vec], `textdata` [@R-textdata], `tidyr` [@R-tidyr], `tidytext` [@R-tidytext], `tm` [@R-tm], `tools` [@R-tools], `topicmodels` [@R-topicmodels], `widyr` [@R-widyr], `word2vec` [@R-word2vec], `wordcloud` [@R-wordcloud], `DiagrammeR` [@R-diagrammeR], and `kableextra` [@R-kableextra].

>>>>

journal: "Social Science & Medicine"
date: "`r Sys.Date()`"
bibliography: bibliography.bib
linenumbers: false
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

@@

Rates of walking and bicycling to school, commonly known as active school travel (AST), have been declining in Canada and the United States for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013], Denmark [@jensenHowObtainHealthy2008], and Japan [@waygoodJapanMaintainingHigh2020]. However, the appetite for AST may be high in many Canadian communities. For instance, 40% of children in a study conducted in Toronto, Ontario who are driven to school would like to travel by bicycle instead [@laroucheRatherBikeSchool2016]. But the study reported that less than 3% actually do, despite the vast majority having access to a bicycle and living within a short and bikeable distance to school. Another study based in London, Ontario reported similar findings with respect to children's preference for active travel [@larsenRouteBasedAnalysisCapture2012]. From a public health perspective, this represents a huge opportunity to improve health and wellbeing if more children could use active modes to school.

In response to this trend, the Government of Ontario, in Canada, created a fund in 2017 to support communities across the province in developing AST initiatives. Green Communities Canada runs the program, called _Ontario Active School Travel_, and determines the projects that will be funded with their support [@GreenCommunities2016]. As of December 2021, OAST has awarded over 2 million Canadian dollars and provided resources for over 25 projects across Ontario.  Many communities implemented school travel planning (STP), along with encouragement activities like walking school buses or developed resources for schools and parents, among other actions [see @GreenCommunitiesProjects]. In this context, STP is a popular "school-specific" intervention led by a facilitator that brings together a committee of stakeholders from diverse sectors including education, planning, transportation, and public health to develop action plans [@buliungSchoolTravelPlanning2011; @mammenSchoolTravelPlanning2014]. The five-step process involves identifying barriers to AST based on the local context and implementing approaches or activities following the 5 E's that alleviate concerns about AST and make AST safer and more convenient [@buliungSchoolTravelPlanning2011; @langUnderstandingModalChoice2011].

@@

More recently, there has been literature exploring the link between transport and children's wellbeing [@waygoodTransportChildrenWellbeing2020], with relevant applications to the study of travel satisfaction [@vandenbergFactorsAffectingParental2020; @westmanChildrenTravelSchool2017]. Being driven to school reduces community interactions for children which may impact their social wellbeing [@waygoodChildrenTravelIncidental2015], whereas walking and bicycling give children opportunities to socialize with friends or siblings [@michailChildrenExperiencesTheir2021]. This is something that children highly value about travel [@zwertsHowChildrenView2010] and indicates that social connections through travel are important for their wellbeing. AST also provides opportunities for children to engage with the natural environment [@fuscoUnderstandingChildrenPerceptions2012; @romeroChildrenExperiencesEnjoyment2015] which can improve their mental or emotional wellbeing.

@@

At the individual level, older child age is often associated with AST [@mammenUnderstandingDriveEscort2012; @starkExploringIndependentActive2018; @wilsonUnderstandingChildParent2018] as parents typically escort younger children. There is evidence that gender is a determinant of AST, with boys being more likely to travel using active modes than girls, although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015]. Children's mode choice to school is strongly influenced by their parents' travel behaviours and the complexity of their household's travel needs [@buliungLivingJourneySchool2021], which indicates that shifting parental perceptions and habits is important. Convenience and inclement weather have been cited by parents as barriers to AST [@buliungSchoolTravelPlanning2011]. Parental perceptions of the built or school environment [@demeesterParentalPerceivedNeighborhood2014; @panterAttitudesSocialSupport2010] and their children's skills [@mammenUnderstandingDriveEscort2012] also influence whether they allow their children to walk or bicycle to school.

Distance between home and school is most strongly associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school. Many studies have also found that the quality of the built environment along the route to school and around the school site [@ikedaAssociationsChildrenActive2018; @rothmanActiveSchoolTransportation2021] and provision of active travel infrastructure [@chenPromotingActiveStudent2018; @pontEnvironmentalCorrelatesChildren2009] facilitate AST. Canadian youth report that they feel most safe bicycling on streets in their neighbourhood or that have low volumes of traffic [@TACbikeinfra2020]. Finally, concerns about traffic and strangers have been reported by parents who drive their children to school [@mammenUnderstandingDriveEscort2012], which highlights that the volume and speed of cars can be a concern or deterrent for AST.

@@

We assembled a collection of publicly available documents that were sourced online from the main stakeholder groups involved in STP initiatives in Ontario: i) school boards (public or Catholic and English-speaking only); ii) municipal governments; and iii) transportation consortia. The latter are a unique group of entities sanctioned by Ontario's Ministry of Education in Ontario 2006. Each consortium involves a collaboration between regions and school boards; the consortium's objective is to deliver more efficient and timely transportation services to schools in each region. Non-profit organizations, police services, and advocacy groups are other stakeholders who often play a role in supporting AST and/or STP, but this study does not include any documents from these groups because they are not consistently participating in all initiatives across Ontario.

@@

kbl(text_tbl,
    booktabs = TRUE,
    caption = "\\label{tab:policy-concordance}The context of key terms that were identified as common bigrams.") %>%
  kable_paper(full_width = F) %>%
  kable_styling(latex_options = c("striped")) %>%
  column_spec(1, bold = T) %>%
  column_spec(3, width = "20em")
```

@@

```{r topics-academic, include=FALSE, cache=TRUE}
#DO NOT RUN EVERY TIME - takes approximately 20 minutes

academic_lda_num <- FindTopicsNumber(
  academic_dtm, 
  topics = seq(from = 2, to = 25, by = 1),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs")
  #control = list(seed = 77),
  #mc.cores = 2L,
  #verbose = TRUE)
```

@@

FindTopicsNumber_plot(municipal_lda_num)
FindTopicsNumber_plot(school_lda_num)
FindTopicsNumber_plot(consortia_lda_num)
FindTopicsNumber_plot(policy_lda_num)
FindTopicsNumber_plot(academic_lda_num)

@@

academic_lda <- LDA(academic_dtm, k = 11, method = "Gibbs", control = NULL, model = NULL)
```

@@

```{r policy-terms, echo=FALSE, out.width="1\\linewidth", fig.cap="\\label{fig:policy-terms}Topics identified in the policy corpus according to clusters of words."}
policy_top_terms <- policy_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -beta)

@@

```{r academic-terms, echo=FALSE, out.width="1\\linewidth", cache=TRUE, fig.cap="\\label{fig:academic-terms}Topics identified in the academic corpus according to clusters of words."}

@@

Finally, we conduct topic modelling to examine the different topics found in the policy and academic corpora. We focus on the policy corpus, instead of individually assessing the municipal, school, and consortia documents, so that we could report on the various frames used across all documents put out by STP stakeholder groups in Ontario. To determine the number of discrete topics in each corpus, we use the _ldatuning_ package. We then use the `LDA` function from the _topicmodels_ package to estimate an LDA model for each group of documents. The parameters from the _ldatuning_ package suggest that the policy corpus has between 7 and 9 topics and the academic corpus has between 17 and 25 topics. After running the LDA model for the academic corpus, it was too difficult to interpret a minimum of 17 topics based on the clusters of words that were identified. We experimented with the model by adjusting and evaluating the number of topics and found that there were 9 distinct topics that could be interpreted, after which there was too much overlap. Figures \ref{fig:policy-terms} and \ref{fig:academic-terms} present the main terms that are associated with the topics found in each corpus.

In the policy corpus, we interpret the following topics based on the cluster of words: (1) resources for walking; (2) walking; (3) supporting active travel; (4) bicycling and the environment; (5) benefits of active travel; (6) safety; and (7) busing information and eligibility. These topics indicate that STP stakeholder groups are sending the message that walking and bicycling to school are healthy travel modes for students, particularly as a means to get physical activity. We also found that there is information shared to support parents and students in using active modes to school such as the availability of cycling lanes or route tips for walking. STP stakeholder groups are appear to be addressing the issue of safety.

The academic corpus has a higher number of topics likely due to the volume of papers that were sourced. The following topics were identified based on the clusters of words: (1) built environment (2) walking distance; (3) AST interventions; (4) parental barriers to walking; (5) behaviours and attitudes; (6) bicycling; (7) social environment; (8) children's independent mobility; (9) modeling trip choice; (10) adolescents and physical activity; and (11) safe routes to school programs. This corpus reflects a broader range of topics than the policy corpus.

@@

Finally, the policy documents discuss proposed solutions to encourage AST. STP stakeholder groups seem to be communicating that AST is possible and safe as a result of improvements to the built environment and available resources for parents and children. A final focus in the policy documents is on various efforts that are underway to support AST including route planning. A few examples include:

@@

Using topic modelling, we analyzed how AST is framed in documents available to the general public on the websites of STP stakeholder groups in Ontario. We found that AST is primarily framed to parents as beneficial to the health and wellbeing of children and to environmental sustainability. This was confirmed by the most common bigrams identified in the policy corpus, as well as the topics identified by the LDA model. The policy documents adequately reflect the evidence that AST contributes positively to children's physical health [see @faulknerActiveSchoolTransport2009; @schoeppeAssociationsChildrenActive2015], although the statements regarding the benefits of AST to children's school performance and cognitive development need to be studied further to produce stronger evidence [@westmanChapterThreeTravel2020]. STP stakeholder groups also communicate that increasing AST may reduce traffic near and around schools. This presumably is communicated to alleviate parental concerns about traffic and safety [@eversParentSafetyPerceptions2014; @mammenUnderstandingDriveEscort2012; @rothmanAssociationsParentsPerception2015; @wilsonUnderstandingChildParent2018] or reduce the frequency of risky behaviours from drivers around schools [@rothmanSchoolEnvironmentStudent2017]. However, the documents do not explain why declining rates of AST are a problem for the particular community or convey any urgency to this issue so that it attracts the attention of parents, the general public, or policy makers. Communicating the potential outcomes of increased AST may be persuasive arguments to motivate behaviour change, but these documents do not appear to encourage parents or the general public to view their behaviour as problematic or unhealthy for their children's development. For example, Canadian parents who escort their children to school have reported concerns about traffic volume around schools [@mammenUnderstandingDriveEscort2012], but may not recognize that their own behaviour contributes to the problem that is perceived to prevent their child from safely walking or bicycling to school [@collinsSafeJourneysEnterprising2001].

The secondary frame of AST that we interpreted based on the LDA model is the opportunity or prospect of behaviour change. STP stakeholder groups identified different ways that parents could encourage or support their child(ren) to commute to school by using active modes. Some school boards and municipalities also shared resources such as walking tip sheets and guidance for starting a walking school bus. Other advice included dropping children off one or two blocks away from school so that they could walk or bike part of the trip. The general emphasis is communicating information that could change parental perceptions about the ease of their children using active modes to school, which may be seen by STP stakeholder groups as a "modifiable" factor [see @riaziCorrelatesChildrenIndependent2019]. In turn, this could encourage parents to modify their routines and incorporate opportunities for their children to use active modes to school.

We found that interpersonal behaviour changes achieved through educational strategies and engineering changes (e.g., traffic calming measures, reduced speed limits, etc.) are communicated to the general public as potential solutions to address the decline of AST. This reflects findings from the AST literature [@panterAttitudesSocialSupport2010], but these solutions have to sufficiently address real and perceived barriers from parents about the household environment and the built environment (see Section 2.2). In most documents, STP stakeholder groups provide parents with resources that help them switch modes for the school commute and/or on reassure them that the built environment has become safer and friendlier to active travelers as a result of infrastructure or policy improvements. As previously noted, the documents do not appear to present a strong "call to action" that urges behaviour change for parents or the general public, which may affect the success of STP interventions. On the other hand, the emphasis on engineering changes may reflect the strong engagement of the "policy stream" [@kingdonAgendasAlternativesPublic1984] and the feasible options to address the problem, since engineering staff and municipal representatives are common STP stakeholders [@buttazzoniSupportingActiveSchool2018; @mammenPuttingSchoolTravel2015].

Given the range of factors that influence AST in a Canadian setting [_inter alia_, see @mammenUnderstandingDriveEscort2012; @mitraIndependentMobilityMode2013; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], STP stakeholder groups must decide which points of intervention that they can reasonably have some influence towards. This would also depend on the local context to ensure that barriers to AST as perceived by parents are addressed. It could be that STP stakeholder groups perceive to have more control over micro-scale elements of the built environment, like traffic calming measures or speed limits, rather "non-modifiable" factors like street density or land use mix. It would certainly be much more difficult for STP stakeholder groups to influence the number of trips to different destinations that households need to make or to intervene in residential location, which affects distance to school. A focus on changing parental perceptions is recommended by many scholars since parents are the "gatekeeper" for children's mobility, but the information communicated by STP stakeholder groups in Ontario should reflect a broader range of factors that influence AST.

@@

There is also a noticeable lack of focus on individual and interpersonal determinants of AST in the policy documents. For example, the role of convenience and inclement weather in shaping household travel decisions [@buliungSchoolTravelPlanning2011] or the age at which children become allowed to travel by active modes or independently [@mammenUnderstandingDriveEscort2012] were not discussed. The desire to escort children to school, which has been noted by parents as a reason to continue driving [@westmanWhatDrivesThem2017], is also not adequately addressed by STP stakeholder groups. The complexity of travel arrangements that must be coordinated by households [see @buliungLivingJourneySchool2021] and the dominant parenting culture to protect children from risk [@riaziChildrenIndependentMobility2018] are likewise overlooked. STP stakeholders may wish to emphasize to parents that older children have greater traffic safety and cognitive abilities to navigate their own routes to school, which could encourage parents to develop their child(ren)'s travel skills over time. Additional attention should be paid to the reasons why parents perceive driving to be more convenient.

Coming back to Kingdon's Multiple Streams Framework [-@kingdonAgendasAlternativesPublic1984], we posited that STP stakeholder groups need to raise awareness about the AST issue among parents and the general public through the problem stream. This could influence perceptions about the issue and encourage behaviour change. Based on the policy documents, it is not obvious that AST has declined significantly over the past few decades in Canada or that this issue merits urgent attention. Many municipalities, schools, and transportation consortia in Ontario use similar content in their public documents about AST. It would be worthwhile for STP stakeholder groups to frame the decline of AST as a "problem" worth addressing with information specific to each local context. STP stakeholders also need to ensure that their communication accounts for the ways in which Canadian parents perceive the built environment in different ways than planners [see @buliungLivingJourneySchool2021]. If there is "conceptual asymmetry" as Buliung et al. [-@buliungLivingJourneySchool2021] identified, the materials disseminated by STP stakeholders may not resonate or reach parents. Future research or STP activities should investigate how parents or the general public respond to messages or information that encourages the adoption of AST and evaluate how effective they are to motivate behaviour change. It would be helpful to know which frames would most encourage behaviour change or increase political support for interventions that address barriers to AST. This type of information could ensure that educational strategies and promotional materials increase buy-in for their target audience.

Although the "policy stream" appears to have been adequately engaged in Ontario communities, it could be that the decline of AST has not been sufficiently framed as "problematic" to warrant more widespread awareness or solutions. If Canadian STP stakeholder groups wish to involve more local residents in their efforts [@buttazzoniSupportingActiveSchool2018], it would also be worthwhile for them to produce different material that communicates why this issue is important to the general public, regardless of whether they currently have children commuting to/from school. The "political steam" could also be further engaged by working with advocacy groups who could attract more support from a broader coalition of individuals.

Finally, Rothman et al. [-@rothmanDeclineActiveSchool2018] note that local solutions to address specific school challenges are needed, and we extend this recommendation to include local context in STP messaging about AST. Instead of generic content about AST, stakeholders involved in STP should produce more information that specifically responds to parents' perceived barriers and challenges that were identified in that local context. For example, STP materials could explain how known concerns in a particular municipality or school area have been addressed through local solutions. This could reflect that solutions have been identified based on what was heard from the community.

@@

A limitation of this study is that we only analyzed texts that were easily accessible to the general public on the websites of STP stakeholder groups in Ontario. Parents likely receive information about AST directly from schools, which may contain more content that reflects the local barriers to AST.

@@

We used text mining and topic modelling to examine how different school travel planning stakeholder (STP) groups in Ontario frame the issue of AST. STP stakeholder groups frame AST as a health and environmental issue that can be addressed through household behaviour change and engineering solutions. Policy documents reveal that STP stakeholder groups are focusing on "modifiable factors" such as parental perceptions or micro-scale elements in the built environment to increase rates of AST. However, AST may not be framed sufficiently as a "problem" that requires urgent intervention, which may impact how parents respond to behaviour change initiatives and limit awareness in the general public. In their public materials about AST, STP stakeholder groups should present solutions for a broader range of factors that influence AST and emphasize why AST rates should increase in local communities.
